Correcting K-correction: dark energy is based on a math error from 1930

### 2025-02-04 paper/dark_energy_corrections.tex
Fix file issues for submission to PRL

@@

@article{lesser2015,
  title={A summary of charge-coupled devices for astronomy},
  author={Lesser, Michael},
  journal={Publications of the Astronomical Society of the Pacific},
  volume={127},
  number={957},
  pages={1097--1104},
  year={2015},
  publisher={The Astronomical Society of the Pacific}
}
\end{filecontents}
\bibliography{references}

>>>>

@article{lesser2015,
  title={A summary of charge-coupled devices for astronomy},
  author={Lesser, Michael},
  journal={Publications of the Astronomical Society of the Pacific},
  volume={127},
  number={957},
  pages={1097--1104},
  year={2015},
  publisher={The Astronomical Society of the Pacific}
}
\end{filecontents}

\begin{filecontents}{dark_energy_corrections.bbl}
\begin{thebibliography}{17}%
\makeatletter
\providecommand \@ifxundefined [1]{%
 \@ifx{#1\undefined}
}%
\providecommand \@ifnum [1]{%
 \ifnum #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \@ifx [1]{%
 \ifx #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \natexlab [1]{#1}%
\providecommand \enquote  [1]{``#1''}%
\providecommand \bibnamefont  [1]{#1}%
\providecommand \bibfnamefont [1]{#1}%
\providecommand \citenamefont [1]{#1}%
\providecommand \href@noop [0]{\@secondoftwo}%
\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
\providecommand \@href[1]{\@@startlink{#1}\@@href}%
\providecommand \@@href[1]{\endgroup#1\@@endlink}%
\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
\providecommand \@@startlink[1]{}%
\providecommand \@@endlink[0]{}%
\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
\providecommand \urlprefix  [0]{URL }%
\providecommand \Eprint [0]{\href }%
\providecommand \doibase [0]{https://doi.org/}%
\providecommand \selectlanguage [0]{\@gobble}%
\providecommand \bibinfo  [0]{\@secondoftwo}%
\providecommand \bibfield  [0]{\@secondoftwo}%
\providecommand \translation [1]{[#1]}%
\providecommand \BibitemOpen [0]{}%
\providecommand \bibitemStop [0]{}%
\providecommand \bibitemNoStop [0]{.\EOS\space}%
\providecommand \EOS [0]{\spacefactor3000\relax}%
\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
\let\auto@bib@innerbib\@empty
%</preamble>
\bibitem [{\citenamefont {Verde}\ \emph {et~al.}(2019)\citenamefont {Verde},
  \citenamefont {Treu},\ and\ \citenamefont {Riess}}]{verde2019}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
  {Verde}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Treu}},\ and\
  \bibinfo {author} {\bibfnamefont {A.~G.}\ \bibnamefont {Riess}},\ }\bibfield
  {title} {\bibinfo {title} {Tensions between the early and late universe},\
  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Nature Astronomy}\
  }\textbf {\bibinfo {volume} {3}},\ \bibinfo {pages} {891} (\bibinfo {year}
  {2019})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Weinberg}(2008)}]{weinberg2008}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Weinberg}},\ }\href@noop {} {\emph {\bibinfo {title} {Cosmology}}}\
  (\bibinfo  {publisher} {OUP Oxford},\ \bibinfo {year} {2008})\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Riess}\ \emph {et~al.}(1998)\citenamefont {Riess},
  \citenamefont {Filippenko}, \citenamefont {Challis}, \citenamefont
  {Clocchiatti}, \citenamefont {Diercks}, \citenamefont {Garnavich},
  \citenamefont {Gilliland}, \citenamefont {Hogan}, \citenamefont {Jha},
  \citenamefont {Kirshner} \emph {et~al.}}]{riess1998}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~G.}\ \bibnamefont
  {Riess}}, \bibinfo {author} {\bibfnamefont {A.~V.}\ \bibnamefont
  {Filippenko}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Challis}},
  \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Clocchiatti}}, \bibinfo
  {author} {\bibfnamefont {A.}~\bibnamefont {Diercks}}, \bibinfo {author}
  {\bibfnamefont {P.~M.}\ \bibnamefont {Garnavich}}, \bibinfo {author}
  {\bibfnamefont {R.~L.}\ \bibnamefont {Gilliland}}, \bibinfo {author}
  {\bibfnamefont {C.~J.}\ \bibnamefont {Hogan}}, \bibinfo {author}
  {\bibfnamefont {S.}~\bibnamefont {Jha}}, \bibinfo {author} {\bibfnamefont
  {R.~P.}\ \bibnamefont {Kirshner}}, \emph {et~al.},\ }\bibfield  {title}
  {\bibinfo {title} {Observational evidence from supernovae for an accelerating
  universe and a cosmological constant},\ }\href@noop {} {\bibfield  {journal}
  {\bibinfo  {journal} {The astronomical journal}\ }\textbf {\bibinfo {volume}
  {116}},\ \bibinfo {pages} {1009} (\bibinfo {year} {1998})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Tolman}(1930)}]{tolman1930}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~C.}\ \bibnamefont
  {Tolman}},\ }\bibfield  {title} {\bibinfo {title} {On the estimation of
  distances in a curved universe with a non-static line element},\ }\href@noop
  {} {\bibfield  {journal} {\bibinfo  {journal} {Proceedings of the National
  Academy of Sciences}\ }\textbf {\bibinfo {volume} {16}},\ \bibinfo {pages}
  {511} (\bibinfo {year} {1930})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {de~Sitter}(1934)}]{desitter1934}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
  {de~Sitter}},\ }\bibfield  {title} {\bibinfo {title} {On distance, magnitude,
  and related quantities in an expanding universe},\ }\href@noop {} {\bibfield
  {journal} {\bibinfo  {journal} {Bulletin of the Astronomical Institutes of
  the Netherlands, Vol. 7, p. 205}\ }\textbf {\bibinfo {volume} {7}},\ \bibinfo
  {pages} {205} (\bibinfo {year} {1934})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Hubble}\ and\ \citenamefont
  {Tolman}(1935)}]{hubble1935}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
  {Hubble}}\ and\ \bibinfo {author} {\bibfnamefont {R.~C.}\ \bibnamefont
  {Tolman}},\ }\bibfield  {title} {\bibinfo {title} {Two methods of
  investigating the nature of the nebular redshift},\ }\href@noop {} {\bibfield
   {journal} {\bibinfo  {journal} {Astrophysical Journal, vol. 82, p. 302}\
  }\textbf {\bibinfo {volume} {82}},\ \bibinfo {pages} {302} (\bibinfo {year}
  {1935})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Oke}\ and\ \citenamefont {Sandage}(1968)}]{oke1968}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~B.}\ \bibnamefont
  {Oke}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Sandage}},\
  }\bibfield  {title} {\bibinfo {title} {Energy distributions, k corrections,
  and the stebbins-whitford effect for giant elliptical galaxies},\ }\href@noop
  {} {\bibfield  {journal} {\bibinfo  {journal} {Astrophysical Journal, vol.
  154, p. 21}\ }\textbf {\bibinfo {volume} {154}},\ \bibinfo {pages} {21}
  (\bibinfo {year} {1968})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Kim}\ \emph {et~al.}(1996)\citenamefont {Kim},
  \citenamefont {Goobar},\ and\ \citenamefont {Perlmutter}}]{kim1996}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
  {Kim}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Goobar}},\ and\
  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Perlmutter}},\ }\bibfield
   {title} {\bibinfo {title} {A generalized k correction for type ia
  supernovae: comparing r-band photometry beyond z= 0.2 with b, v, and r-band
  nearby photometry},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
  {journal} {Publications of the Astronomical Society of the Pacific}\ }\textbf
  {\bibinfo {volume} {108}},\ \bibinfo {pages} {190} (\bibinfo {year}
  {1996})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Planck-Collaboration}\ \emph
  {et~al.}(2016)\citenamefont {Planck-Collaboration}, \citenamefont {Ade},
  \citenamefont {Aghanim}, \citenamefont {Arnaud}, \citenamefont {Ashdown},
  \citenamefont {Aumont}, \citenamefont {Baccigalupi}, \citenamefont {Banday},
  \citenamefont {Barreiro}, \citenamefont {Bartlett}, \citenamefont {Bartolo}
  \emph {et~al.}}]{planck2015}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibnamefont {Planck-Collaboration}},
  \bibinfo {author} {\bibfnamefont {P.~A.}\ \bibnamefont {Ade}}, \bibinfo
  {author} {\bibfnamefont {N.}~\bibnamefont {Aghanim}}, \bibinfo {author}
  {\bibfnamefont {M.}~\bibnamefont {Arnaud}}, \bibinfo {author} {\bibfnamefont
  {M.}~\bibnamefont {Ashdown}}, \bibinfo {author} {\bibfnamefont
  {J.}~\bibnamefont {Aumont}}, \bibinfo {author} {\bibfnamefont
  {C.}~\bibnamefont {Baccigalupi}}, \bibinfo {author} {\bibfnamefont
  {A.}~\bibnamefont {Banday}}, \bibinfo {author} {\bibfnamefont
  {R.}~\bibnamefont {Barreiro}}, \bibinfo {author} {\bibfnamefont
  {J.}~\bibnamefont {Bartlett}}, \bibinfo {author} {\bibfnamefont
  {N.}~\bibnamefont {Bartolo}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo
  {title} {Planck 2015 results-xiii. cosmological parameters},\ }\href@noop {}
  {\bibfield  {journal} {\bibinfo  {journal} {Astronomy \& Astrophysics}\
  }\textbf {\bibinfo {volume} {594}},\ \bibinfo {pages} {A13} (\bibinfo {year}
  {2016})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Perlmutter}\ \emph {et~al.}(1999)\citenamefont
  {Perlmutter}, \citenamefont {Aldering}, \citenamefont {Goldhaber},
  \citenamefont {Knop}, \citenamefont {Nugent}, \citenamefont {Castro},
  \citenamefont {Deustua}, \citenamefont {Fabbro}, \citenamefont {Goobar},
  \citenamefont {Groom} \emph {et~al.}}]{perlmutter1999}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
  {Perlmutter}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
  {Aldering}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Goldhaber}},
  \bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont {Knop}}, \bibinfo
  {author} {\bibfnamefont {P.}~\bibnamefont {Nugent}}, \bibinfo {author}
  {\bibfnamefont {P.~G.}\ \bibnamefont {Castro}}, \bibinfo {author}
  {\bibfnamefont {S.}~\bibnamefont {Deustua}}, \bibinfo {author} {\bibfnamefont
  {S.}~\bibnamefont {Fabbro}}, \bibinfo {author} {\bibfnamefont
  {A.}~\bibnamefont {Goobar}}, \bibinfo {author} {\bibfnamefont {D.~E.}\
  \bibnamefont {Groom}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo {title}
  {Measurements of $\omega$ and $\lambda$ from 42 high-redshift supernovae},\
  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The Astrophysical
  Journal}\ }\textbf {\bibinfo {volume} {517}},\ \bibinfo {pages} {565}
  (\bibinfo {year} {1999})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {DES-Collaboration}\ \emph {et~al.}(2024)\citenamefont
  {DES-Collaboration}, \citenamefont {Abbott}, \citenamefont {Acevedo},
  \citenamefont {Aguena}, \citenamefont {Alarcon}, \citenamefont {Allam},
  \citenamefont {Alves}, \citenamefont {Amon}, \citenamefont
  {Andrade-Oliveira}, \citenamefont {Annis}, \citenamefont {Armstrong} \emph
  {et~al.}}]{abbott2024}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibnamefont {DES-Collaboration}},
  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Abbott}}, \bibinfo
  {author} {\bibfnamefont {M.}~\bibnamefont {Acevedo}}, \bibinfo {author}
  {\bibfnamefont {M.}~\bibnamefont {Aguena}}, \bibinfo {author} {\bibfnamefont
  {A.}~\bibnamefont {Alarcon}}, \bibinfo {author} {\bibfnamefont
  {S.}~\bibnamefont {Allam}}, \bibinfo {author} {\bibfnamefont
  {O.}~\bibnamefont {Alves}}, \bibinfo {author} {\bibfnamefont
  {A.}~\bibnamefont {Amon}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
  {Andrade-Oliveira}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {Annis}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Armstrong}},
  \emph {et~al.},\ }\bibfield  {title} {\bibinfo {title} {The dark energy
  survey: Cosmology results with $\sim$1500 new high-redshift type ia
  supernovae using the full 5-year dataset},\ }\href@noop {} {\bibfield
  {journal} {\bibinfo  {journal} {arXiv preprint arXiv:2401.02929}\ } (\bibinfo
  {year} {2024})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Flaugher}\ \emph {et~al.}(2015)\citenamefont
  {Flaugher}, \citenamefont {Diehl}, \citenamefont {Honscheid}, \citenamefont
  {Abbott}, \citenamefont {Alvarez}, \citenamefont {Angstadt}, \citenamefont
  {Annis}, \citenamefont {Antonik}, \citenamefont {Ballester}, \citenamefont
  {Beaufore} \emph {et~al.}}]{flaugher2015}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
  {Flaugher}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Diehl}},
  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Honscheid}}, \bibinfo
  {author} {\bibfnamefont {T.}~\bibnamefont {Abbott}}, \bibinfo {author}
  {\bibfnamefont {O.}~\bibnamefont {Alvarez}}, \bibinfo {author} {\bibfnamefont
  {R.}~\bibnamefont {Angstadt}}, \bibinfo {author} {\bibfnamefont
  {J.}~\bibnamefont {Annis}}, \bibinfo {author} {\bibfnamefont
  {M.}~\bibnamefont {Antonik}}, \bibinfo {author} {\bibfnamefont
  {O.}~\bibnamefont {Ballester}}, \bibinfo {author} {\bibfnamefont
  {L.}~\bibnamefont {Beaufore}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo
  {title} {The dark energy camera},\ }\href@noop {} {\bibfield  {journal}
  {\bibinfo  {journal} {The Astronomical Journal}\ }\textbf {\bibinfo {volume}
  {150}},\ \bibinfo {pages} {150} (\bibinfo {year} {2015})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Lesser}(2015)}]{lesser2015}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Lesser}},\ }\bibfield  {title} {\bibinfo {title} {A summary of
  charge-coupled devices for astronomy},\ }\href@noop {} {\bibfield  {journal}
  {\bibinfo  {journal} {Publications of the Astronomical Society of the
  Pacific}\ }\textbf {\bibinfo {volume} {127}},\ \bibinfo {pages} {1097}
  (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Burns}\ \emph {et~al.}(2010)\citenamefont {Burns},
  \citenamefont {Stritzinger}, \citenamefont {Phillips}, \citenamefont
  {Kattner}, \citenamefont {Persson}, \citenamefont {Madore}, \citenamefont
  {Freedman}, \citenamefont {Boldt}, \citenamefont {Campillay}, \citenamefont
  {Contreras} \emph {et~al.}}]{burns2010}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~R.}\ \bibnamefont
  {Burns}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Stritzinger}},
  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Phillips}}, \bibinfo
  {author} {\bibfnamefont {S.}~\bibnamefont {Kattner}}, \bibinfo {author}
  {\bibfnamefont {S.}~\bibnamefont {Persson}}, \bibinfo {author} {\bibfnamefont
  {B.~F.}\ \bibnamefont {Madore}}, \bibinfo {author} {\bibfnamefont {W.~L.}\
  \bibnamefont {Freedman}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
  {Boldt}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Campillay}},
  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Contreras}}, \emph
  {et~al.},\ }\bibfield  {title} {\bibinfo {title} {The carnegie supernova
  project: light-curve fitting with snoopy},\ }\href@noop {} {\bibfield
  {journal} {\bibinfo  {journal} {The Astronomical Journal}\ }\textbf {\bibinfo
  {volume} {141}},\ \bibinfo {pages} {19} (\bibinfo {year} {2010})}\BibitemShut
  {NoStop}%
\bibitem [{\citenamefont {Kessler}\ \emph {et~al.}(2009)\citenamefont
  {Kessler}, \citenamefont {Bernstein}, \citenamefont {Cinabro}, \citenamefont
  {Dilday}, \citenamefont {Frieman}, \citenamefont {Jha}, \citenamefont
  {Kuhlmann}, \citenamefont {Miknaitis}, \citenamefont {Sako}, \citenamefont
  {Taylor} \emph {et~al.}}]{kessler2009}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
  {Kessler}}, \bibinfo {author} {\bibfnamefont {J.~P.}\ \bibnamefont
  {Bernstein}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Cinabro}},
  \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Dilday}}, \bibinfo
  {author} {\bibfnamefont {J.~A.}\ \bibnamefont {Frieman}}, \bibinfo {author}
  {\bibfnamefont {S.}~\bibnamefont {Jha}}, \bibinfo {author} {\bibfnamefont
  {S.}~\bibnamefont {Kuhlmann}}, \bibinfo {author} {\bibfnamefont
  {G.}~\bibnamefont {Miknaitis}}, \bibinfo {author} {\bibfnamefont
  {M.}~\bibnamefont {Sako}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Taylor}}, \emph {et~al.},\ }\bibfield  {title} {\bibinfo {title} {Snana: A
  public software package for supernova analysis},\ }\href@noop {} {\bibfield
  {journal} {\bibinfo  {journal} {Publications of the Astronomical Society of
  the Pacific}\ }\textbf {\bibinfo {volume} {121}},\ \bibinfo {pages} {1028}
  (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Vincenzi}\ \emph {et~al.}(2024)\citenamefont
  {Vincenzi}, \citenamefont {Brout}, \citenamefont {Armstrong}, \citenamefont
  {Popovic}, \citenamefont {Taylor}, \citenamefont {Acevedo}, \citenamefont
  {Camilleri}, \citenamefont {Chen}, \citenamefont {Davis}, \citenamefont {Lee}
  \emph {et~al.}}]{vincenzi2024}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
  {Vincenzi}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Brout}},
  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Armstrong}}, \bibinfo
  {author} {\bibfnamefont {B.}~\bibnamefont {Popovic}}, \bibinfo {author}
  {\bibfnamefont {G.}~\bibnamefont {Taylor}}, \bibinfo {author} {\bibfnamefont
  {M.}~\bibnamefont {Acevedo}}, \bibinfo {author} {\bibfnamefont
  {R.}~\bibnamefont {Camilleri}}, \bibinfo {author} {\bibfnamefont
  {R.}~\bibnamefont {Chen}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
  {Davis}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Lee}}, \emph
  {et~al.},\ }\bibfield  {title} {\bibinfo {title} {The dark energy survey
  supernova program: Cosmological analysis and systematic uncertainties},\
  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {The Astrophysical
  Journal}\ }\textbf {\bibinfo {volume} {975}},\ \bibinfo {pages} {86}
  (\bibinfo {year} {2024})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Planck-Collaboration}\ \emph
  {et~al.}(2020)\citenamefont {Planck-Collaboration}, \citenamefont {Aghanim},
  \citenamefont {Akrami}, \citenamefont {Ashdown}, \citenamefont {Aumont},
  \citenamefont {Baccigalupi}, \citenamefont {Ballardini}, \citenamefont
  {Banday}, \citenamefont {Barreiro}, \citenamefont {Bartolo}, \citenamefont
  {Basak} \emph {et~al.}}]{planck2020}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibnamefont {Planck-Collaboration}},
  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Aghanim}}, \bibinfo
  {author} {\bibfnamefont {Y.}~\bibnamefont {Akrami}}, \bibinfo {author}
  {\bibfnamefont {M.}~\bibnamefont {Ashdown}}, \bibinfo {author} {\bibfnamefont
  {J.}~\bibnamefont {Aumont}}, \bibinfo {author} {\bibfnamefont
  {C.}~\bibnamefont {Baccigalupi}}, \bibinfo {author} {\bibfnamefont
  {M.}~\bibnamefont {Ballardini}}, \bibinfo {author} {\bibfnamefont {A.~J.}\
  \bibnamefont {Banday}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
  {Barreiro}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Bartolo}},
  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Basak}}, \emph {et~al.},\
  }\bibfield  {title} {\bibinfo {title} {Planck 2018 results-vi. cosmological
  parameters},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
  {Astronomy \& Astrophysics}\ }\textbf {\bibinfo {volume} {641}},\ \bibinfo
  {pages} {A6} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
\end{thebibliography}%
\end{filecontents}

@@

\bibliography{references}
